---
title: "Evidence from systematic literature review"
params:
    agent: "agent"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    self_contained: false

---
<style type="text/css">

body{
  font-family: Verdana;
  font-size: 12pt;
}

.navbar {
  background-color:#1DAF8E;
}

.bggreen {
  background-color: #1DAF8E;
}

/* Headers */
h1{
  font-family: Verdana;
  font-size: 16pt;
  font-weight: bold; 
  color: white;
}

.chart-title {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li.active a {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
    font-size: 16pt;
}


</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, fig.width=10,fig.height=6)
library(plotly)
library(dplyr)
library(stringr)
library(knitr)
library(gdata)
library(kableExtra)
library(DT)
library(flexdashboard)

source("Functions.r")


dfva <- read.csv("../data/FilesDownload/Vaccines_cleaned.csv")
references <- read.csv("../data/FilesDownload/Vaccines_refid.csv")

agent <- params$agent 

# source("SLR_objectives/Functions.r")
# dfva <- read.csv("data/FilesDownload/Vaccines_cleaned.csv")
# references <- read.csv("data/FilesDownload/Vaccines_refid.csv")
# agent = agents[a]


dfDZ <- dfva[dfva$agent==agent,]


dfDZ$targetSpecies <- gsub("\\s*\\([^\\)]+\\)","",as.character(dfDZ$targetSpecies))
dfDZ <- species.name.cleanup(data=dfDZ)

references$targetSpecies<- gsub("\\s*\\([^\\)]+\\)","",as.character(references$targetSpecies))
references <- species.name.cleanup(data=references)


dfDZ$targetSpecies <- as.factor(dfDZ$targetSpecies)


plots.font <- list(
  family="Verdana",
  size=16
)


dzeff <- dfDZ[which(!is.na(dfDZ$efficacy)),]


#table(dfDZ$targetSpecies)
```




Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Reported Vaccine efficacy </h1>


Row
-----------------------------------------------------------------------
###
A total of `r length(unique(dfDZ$refID))` references were reviewed, but only `r length(unique(dzeff$refID))` reported vaccine efficacy. The results per species are presented in the table below. 

The other references, and the species they studied, are listed further below in the complete reference list.

In the next round of updates of the systematic literature reviews for vaccines (planned for 2022), outcomes other than efficacy will be summarized and displayed in this story map. 


Row{data-height=600}
-----------------------------------------------------------------------

```{r}
options(DT.options = list(scrollY="100vh",pageLength =5))
datatable(dzeff[,c("refID","targetSpecies","testSubstanceCAT",
                    "efficacy","UCI_efficacy","LCI_efficacy","dose","dosageFreq","dosageInterval",
                    "labTest")])

```
 



Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;REFERENCES </h1>


Row
-----------------------------------------------------------------------
###
In the left panel you can find information about the entire systematic literature review. The specific references for this agent, and used in this section of the story map are listed below.

Row{data-height=600}
-----------------------------------------------------------------------

```{r references}
options(DT.options = list(scrollY="100vh",pageLength =5))
datatable(unique(references[references$Refid%in%dfDZ$refID,c(1,3,5)]), filter = 'top', rownames=FALSE)

```
 
 
