---
title: "Evidence from systematic literature review"
params:
    styling: TRUE
    agent: "agent"
    min.groups.plot: 1
    agent.subtype: "agentSubtype"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    self_contained: false

---
<style type="text/css">

body{
  font-family: Verdana;
  font-size: 12pt;
}

.navbar {
  background-color:#1DAF8E;
}

.bggreen {
  background-color: #1DAF8E;
}

/* Headers */
h1{
  font-family: Verdana;
  font-size: 16pt;
  font-weight: bold; 
  color: white;
}

.chart-title {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li.active a {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
    font-size: 16pt;
}


</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, fig.width=10,fig.height=6)
library(tidyr)
library(wordcloud)
library(RColorBrewer)
#library(wordcloud2)
library(tm)

library(plotly)
library(dplyr)
library(stringr)
library(knitr)
library(gdata)
library(kableExtra)
library(DT)
library(flexdashboard)
library(scales) 
library(ggplot2)
library(shiny)

#library(devtools)
#devtools::install_github("lchiffon/wordcloud2")
library(wordcloud2)


source("Functions.r")
#source("Metaanalysis_functions.r")

dfgd <- read.csv("../data/FilesDownload/GeoDistribution_cleaned.csv")
references <- read.csv("../data/FilesDownload/GeoDistribution_refid.csv")

agent <- params$agent
styling <- params$styling
min.groups.plot <- params$min.groups.plot
agent.subtype <- params$agent.subtype

# styling=T
# min.groups.plot=1
# agent = agents[a]
# agent.subtype <- agent.subtypes[a]

#agent = "Rift Valley fever virus"

dfDZ <- dfgd[dfgd$agent==agent,]


dfDZ$targetSpecies <- gsub("\\s*\\([^\\)]+\\)","",as.character(dfDZ$targetSpecies))
dfDZ <- species.name.cleanup(data=dfDZ)

references$targetSpecies<- gsub("\\s*\\([^\\)]+\\)","",as.character(references$targetSpecies))
references <- species.name.cleanup(data=references)


dfDZ$targetSpecies <- as.factor(dfDZ$targetSpecies)

plots.font <- list(
  family="Verdana",
  size=16
)

dfDZ.pos <- dfDZ[which(dfDZ$nPositive!=0),]
if (length(which(is.na(dfDZ.pos$nPositive)))>0&length(which(is.na(dfDZ.pos$prevalence)))>0){
dfDZ.pos <- dfDZ.pos[-which(is.na(dfDZ.pos$nPositive)&is.na(dfDZ.pos$prevalence)),]
}


unique.sp <- unique(as.character(dfDZ$targetSpecies))
unique.sp <- unique.sp[-which(unique.sp=="not investigated/not given/not relevant")]
unique.sp <- unique.sp[-which(unique.sp=="Other")]

unique.sp.pos <- unique(as.character(dfDZ.pos$targetSpecies))
unique.sp.pos <- unique.sp.pos[-which(unique.sp.pos=="not investigated/not given/not relevant")]
unique.sp.pos <- unique.sp.pos[-which(unique.sp.pos=="Other")]

unique.sp.neg <- unique.sp[!unique.sp%in%unique.sp.pos]

#table(dfDZ$targetSpecies)
```


Row
-----------------------------------------------------------------------


###  {.bggreen data-width=150}
<h1>Host species</h1>


###
Disease was demonstrated in the following animal species:

<b>  `r trimws(sort(unique.sp.pos),which="right")`</b>.

Studies included in the literature review also tested, without following any confirmed cases, the following species: <b>  `r trimws(sort(unique.sp.neg),which="right")`</b>.





```{r}
# Row
# -----------------------------------------------------------------------
# ###  {.bgorange}
# 
# <h1>WORK IN PROGRESS!</h1>
# This section of the disease profiles in currently under construction, we will keep updating and improving this under the remainder of 2022.  
# 

```



Row{data-height=550}
-----------------------------------------------------------------------

###  {.bggreen data-width=150}

<h1>Most frequent clinical signs</h1>


<!-- Button trigger modal -->
<button type="button" class="btn btn-link" data-toggle="modal" data-target="#csWC">
<img src=../../../../templates/assets/css/images/info.png>
</button>

<!-- Modal -->
<div class="modal fade" id="csWC" tabindex="-1" role="dialog" aria-labelledby="exampleModalLabel" aria-hidden="true">
<div class="modal-dialog" role="document">
<div class="modal-content">
<div class="modal-body">

The Word cloud was constructed based on the clinical signs reported in all studies reviewed. 
<br>
Hover the mouse over the words to see the number of animal groups in which the clinical sign was reported, from all reviewed. The total number
of animal groups and studies are reported further below.
<br>
One animal group is defined as a unique group of animals, within the study, which were subjected to the same experimental or field conditions.
For example, an outbreak report which reports the number of positive animals of two different species, is likely to report these are
two independent animal groups. But more groups could be define din the study if for instance the number of affected animals is reported
separately for different age categories.
</div>
<div class="modal-footer">
<button type="button" class="btn btn-secondary" data-dismiss="modal">Close</button>
</div>
</div>
</div>
</div>



### 

```{r wordcloud, message=FALSE, warning=FALSE, results='asis'}

text <- dfDZ %>%
    select(clinicalSigns) %>%
    #mutate(clinicalSigns = str_replace_all(clinicalSigns))
    mutate_all(na_if,"") %>%
    na.omit() 

# Create a corpus
docs <- Corpus(VectorSource(text))


docs <- docs %>%
    tm_map(removeNumbers) %>%
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("disc", "optic", "among", "confirmed", "confirmedncases", "cases", "high", "nand", "macular", "ocular", "fevern", "symptomatic"))

dtm <- TermDocumentMatrix(docs)
matrix <- as.matrix(dtm)
words <- sort(rowSums(matrix),decreasing=TRUE)
df <- data.frame(word = names(words),freq=words)


 df$word <- as.factor(df$word)
 wordcloud2(df[(df$freq>3),], size=6,minSize=1)


```

Row
-----------------------------------------------------------------------

### 

The table below lists all references which reported clinical signs or severity. You can sort columns (for instance by species)

```{r}
#dfDZ$targetSpecies
#unique(dfDZ$clinicalSigns)
#unique(dfDZ$severity)

 options(DT.options = list(scrollY="100vh",pageLength =10))
datatable(unique(dfDZ[!((dfDZ$clinicalSigns=="")&(dfDZ$severity=="")),c("targetSpecies","clinicalSigns","severity")]))

```



Row{data-height=650}
-----------------------------------------------------------------------

###  {.bggreen data-width=150}


<h1>Study context</h1>


<!-- Button trigger modal -->
<button type="button" class="btn btn-link" data-toggle="modal" data-target="#stContext">
<img src=../../../../templates/assets/css/images/info.png>
</button>

<!-- Modal -->
<div class="modal fade" id="stContext" tabindex="-1" role="dialog" aria-labelledby="exampleModalLabel" aria-hidden="true">
<div class="modal-dialog" role="document">
<div class="modal-content">
<div class="modal-body">

These are the number of studies reviewed up until the last update of the literature review. 
Consult the notes on the left for details about the study protocol and eligibility criteria.
One animal group is defined as a unique group of animals, within the study, which were subjected to the same experimental or field conditions.
For example, an outbreak report which reports the number of positive animals of two different species, is likely to report these are
two independent animal groups. But more groups could be define din the study if for instance the number of affected animals is reported
separately for different age categories.

</div>
<div class="modal-footer">
<button type="button" class="btn btn-secondary" data-dismiss="modal">Close</button>
</div>
</div>
</div>
</div>



###

```{r types of studies, message=FALSE, warning=FALSE}
 
total.gps <- dfDZ %>% 
  group_by(refID, groupID) %>% nrow()

total.papers <- n_distinct(dfDZ$refID)

total.countries <- n_distinct(dfDZ$country)

total.regions <- n_distinct(dfDZ$sampArea)


# dfbind <- cbind(dfgd$refID,dfgd$studyContext)
# dfbind <- dfbind[!duplicated(dfbind),]
# 
# total.papers <- sum(!duplicated(dfgd$refID))
# total.gps <- dim(dfbind)[1]

```
The systematic literature review included a total of `r total.papers` articles for this agent. Data was retrieved from `r total.countries` countries.To see this information in a map, please refer to the "Field studies" tab in the menu at the top of this animal disease profile.  


```{r}

#Replacing the wrong string for a dash; summing the amount of papers per types of study. NAs have been added to 'Unspecified'.
#table(dfDZ$studyContext)

dfDZ$studyContext[dfDZ$studyContext=="Monitoring &ndash;active"]<- "Active surveillance"
dfDZ$studyContext[dfDZ$studyContext=="Surveillance active (active search for cases)"]<- "Active surveillance"
dfDZ$studyContext[dfDZ$studyContext=="Surveillance passive (follow up reports)"]<- "Passive surveillance"

  
dftypesstudies <- dfDZ %>%
  mutate(studyContext = str_replace(studyContext, " &ndash;", " - "),
         studyContext = na_if(studyContext, ""),
         studyContext = replace_na(studyContext, "Unspecified")) %>%
  group_by(studyContext) %>%
  summarize(npapers = n_distinct(refID)) %>%
  arrange(studyContext) %>%
  #na.omit() %>% 
  rename(
    "Study context" = studyContext,
    "Number of papers" = npapers,
  )

 # dftypesstudies <- head(dftypesstudies)
 # knitr::kable(dftypesstudies, col.names = gsub("[.]", " ", names(dftypesstudies)))

dftypesstudies.g <- dfDZ %>%
  mutate(studyContext = str_replace(studyContext, " &ndash;", " - "),
         studyContext = na_if(studyContext, ""),
         studyContext = replace_na(studyContext, "Unspecified")) %>%
  group_by(studyContext) %>%
  summarize(npapers = n_distinct(refID,groupID)) %>%
  arrange(studyContext) %>%
  #na.omit() %>% 
  rename(
    "Study context" = studyContext,
    "Number of groups" = npapers,
  )

dftypesstudies<-cbind(dftypesstudies,dftypesstudies.g$`Number of groups`)
colnames(dftypesstudies) <- c("Study context","Number of papers","Number of animal groups")

dftypesstudies <- dftypesstudies[order(dftypesstudies$`Number of papers`,decreasing=T),]


other <- which(dftypesstudies$`Study context`=="Other")
unspec <- which(dftypesstudies$`Study context`=="Unspecified")
last <- c(other,unspec)

dftypesstudies <- rbind(dftypesstudies[-last,],dftypesstudies[last,])

kable(dftypesstudies, align="c",row.names = F)%>%
    kable_material(c("striped", "hover"))
```




Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Outbreak investigations </h1>


```{r, results='asis'}
if(length(which(dftypesstudies=="Outbreak investigation"))>0){
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
  cat("\nFor official data on reported outbreaks, please visit the \"Geographical distribution section\" of this animal disease profile (menu on the top of the page).\n")
  cat("<br>")
   cat(paste0("\nBelow we summarize information from the ",dftypesstudies$`Number of papers`[dftypesstudies$`Study context`=="Outbreak investigation"]," references included in the literature review which referred to outbreak investigations. \n"))
    cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")

}else{
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat("\nNone of the references included in the systematic literature review declared the study type to be \"Outbreak investigation\".\n")
   cat("<br>")
cat("\nFor official data on reported outbreaks, please visit the \"Geographical distribution section\" of this animal disease profile (menu on the top of the page).\n")
}

```



```{r outbreak.years,fig.height=4,  message=FALSE, warning=FALSE}

#if(length(which(dftypesstudies=="Outbreak investigation"))>0){

   dfOutbreaks <- dfDZ[dfDZ$studyContext=="Outbreak investigation",]
   
   dfOutbreaks.year <-dfOutbreaks[,c("refID", "startYear")]
   dfOutbreaks.year <- unique(dfOutbreaks.year)
   
   complete.year <- seq(min(dfOutbreaks.year$startYear),max(dfOutbreaks.year$startYear))
   add.years <- data.frame(
     startYear = complete.year[!(complete.year%in%dfOutbreaks.year$startYear)],
     npapers = 0
     )
   
   
   dfOutbreaks.year <- dfOutbreaks.year  %>%
                group_by(startYear) %>%
                summarize(npapers = n_distinct(refID))
   
   dfOutbreaks.year <- rbind(dfOutbreaks.year,add.years)
     dfOutbreaks.year <- dfOutbreaks.year[order(dfOutbreaks.year$startYear),]
   
   
       p <- plot_ly(dfOutbreaks.year, x = ~startYear, y = ~npapers, type = 'bar')%>%
      layout(#title = 'Number of papers per year reported as start of study/outbreak',
        yaxis = list(title = 'Number of references'),
             xaxis = list(tickangle=-45, title="Start year"),
             barmode = 'group')

   p%>% layout(font=plots.font)
     
     #######
     ##### keep only TABLES until fix the wordcloud issue
     ######
   
#}
```

Row
-----------------------------------------------------------------------

### 
```{r}
outbreaks <-  dfDZ %>%
    filter(studyContext == "Outbreak investigation") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody", 
           TRUE ~ as.character(labTarget))) %>%
    select( #add here variables to be displayed
      country,
      startYear,
      targetSpecies,
      labTarget,
      sampUnitSize,
      nPositive,
      prevalence
    ) %>% 
    distinct() %>% #keeping only distinct rows 
    arrange (desc(startYear), targetSpecies, .by_group= TRUE)
           
outbreaks$sampUnitSize <- as.numeric(outbreaks$sampUnitSize)
outbreaks$nPositive     <- as.numeric(outbreaks$nPositive    )
outbreaks$prevalence        <- as.numeric(outbreaks$prevalence       )


               outbreaks1 <- aggregate(outbreaks$sampUnitSize , by=list(outbreaks$country,outbreaks$startYear,
                                                         outbreaks$targetSpecies,outbreaks$labTarget),
                                       FUN=sum,na.rm=T)
               outbreaks2 <- aggregate(outbreaks$nPositive , by=list(outbreaks$country,outbreaks$startYear,
                                                         outbreaks$targetSpecies,outbreaks$labTarget),
                                       FUN=sum,na.rm=T)
               outbreaks3 <- aggregate(outbreaks$prevalence    , by=list(outbreaks$country,outbreaks$startYear,
                                                         outbreaks$targetSpecies,outbreaks$labTarget),
                                       FUN=mean,na.rm=T)
      
           
               outbreaks <- cbind(outbreaks1,outbreaks2[,"x"],round(outbreaks3[,"x"],1))
               colnames(outbreaks) <- c("Country","Start Year","Target Species", "Lab target","n Tested","n Pos","prevalence")
               
               outbreaks$`Target Species`<-str_replace(outbreaks$`Target Species`,"not investigated/not given/not relevant","")
              outbreaks$`Lab target`<-str_replace(outbreaks$`Lab target`,"not investigated/not given/not relevant","")

              outbreaks <- outbreaks[order(outbreaks$`Target Species`),]
              outbreaks <- outbreaks[order(outbreaks$`Start Year`,decreasing=TRUE),]
               
  # kable(outbreaks, align="c",row.names = F)%>%
  #    kable_material(c("striped", "hover"))
  
  
              options(DT.options = list(scrollY="100vh",pageLength =10))

              datatable(outbreaks,
              filter = "none", 
            rownames = F,
            colnames = c("Country",
                         "Start year",
                         "Target species",
                         "Lab target",
                         "n tested",
                         "n pos",
                         "prevalence"))

```




Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Clinical investigations</h1>

Row
-----------------------------------------------------------------------

###

```{r Clinical investigations}
#clinicalinvestigation <- datatable(
 clinical <- dfDZ %>%
    filter(studyContext == "Clinical investigations") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody",
           TRUE ~ as.character(labTarget))) %>%
    select( #add here variables to be displayed
      refID,
      targetSpecies,
      sampUnitSize,
      clinicalSigns,
      severity
    ) %>%
    distinct() %>% #keeping only distinct rows
    arrange (desc(refID), targetSpecies, .by_group= TRUE)

options(DT.options = list(scrollY="100vh",pageLength =10))

datatable(clinical,
            filter = "none", 
            rownames = F,
            colnames = c("refID","Target species","group size","Clinical Signs","Severity"))

#Run this if the datatable does not work. Just need to delete the datatable() function from the vector first, and then run it again. Might be necessary to adjust height afterwards. 

#  kable(clinicalinvestigation, align="c",row.names = F)%>%
#    kable_material(c("striped", "hover"))
```




Row{data-height=80 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Passive Surveillance</h1>

Row{data-height=800}
-----------------------------------------------------------------------

###


```{r Surveillance - passive}
passive <- dfDZ %>%
    filter(studyContext == "Passive surveillance") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody", 
           TRUE ~ as.character(labTarget))) %>%
    select(
      refID,
      country,
      startYear,
      targetSpecies,
      sampPoint,
      reasonSampling,
      sampStrategy,
      matrix,
      labTarget,
      sampUnitSize,
      nPositive,
      prevalence
    ) %>% 
    distinct() %>% #keeping only distinct rows 
    arrange (desc(refID), targetSpecies, .by_group= TRUE)#, 


options(DT.options = list(scrollY="100vh",pageLength =10))

datatable(passive,
            filter = "none", 
            rownames = F,
            colnames = c("refID","Country","Year","Target species",
                         "Sampling Point", "Reason for sampling", "Sampling strategy",
                         "matrix","Lab target","sample size","n Pos","prevalence"))

# kable(surveillance, align="c",row.names = F)%>%
#   kable_material(c("striped", "hover"))


```




Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Proof of disease freedom</h1>

Row
-----------------------------------------------------------------------

###

```{r dz.freedom}
dzfreedom <- dfDZ %>%
    filter(studyContext == "Proof of disease freedom") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody",
           TRUE ~ as.character(labTarget))) %>%
    select(
      refID,
      country,
      startYear,
      targetSpecies,
      sampPoint,
      sampStrategy,
      matrix,
      labTarget,
      sampUnitSize
      ) %>% 
    distinct() %>% #keeping only distinct rows 
    arrange (desc(refID), targetSpecies, .by_group= TRUE)#, 


options(DT.options = list(scrollY="100vh",pageLength =10))

datatable(dzfreedom,
            filter = "none", 
            rownames = F,
            colnames = c("refID","Country","Year","Target species",
                         "Sampling Point", "Sampling strategy",
                         "matrix","Lab target","sample size"))

#Run this if the datatable does not work. Just need to delete the datatable() function from the vector first, and then run it again. Might be necessary to adjust height afterwards. 

#  kable(clinicalinvestigation, align="c",row.names = F)%>%
#    kable_material(c("striped", "hover"))
```






Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Observational study</h1>

Row{data-height=800}
-----------------------------------------------------------------------

###



```{r Observational study}
observational <- dfDZ %>%
    filter(studyContext == "Observational study (case control, cohort)") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody", 
           TRUE ~ as.character(labTarget))) %>%
    select(
      refID,
      country,
      startYear,
      targetSpecies,
      sampPoint,
      reasonSampling,
      sampStrategy,
      matrix,
      labTarget,
      sampUnitSize,
      nPositive,
      prevalence
    ) %>% 
    distinct() %>% #keeping only distinct rows 
    arrange (desc(refID), targetSpecies, .by_group= TRUE)#, 


options(DT.options = list(scrollY="100vh",pageLength =10))

datatable(observational,
            filter = "none", 
            rownames = F,
            colnames = c("refID","Country","Year","Target species",
                         "Sampling Point", "Reason for sampling", "Sampling strategy",
                         "matrix","Lab target","sample size","n Pos","prevalence"))


```



Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Active surveillance</h1>

Row{data-height=800}
-----------------------------------------------------------------------

###



```{r active surveillance}
active <- dfDZ %>%
    filter(studyContext == "Active surveillance") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody", 
           TRUE ~ as.character(labTarget))) %>%
    select(
      refID,
      country,
      startYear,
      targetSpecies,
      sampPoint,
      reasonSampling,
      sampStrategy,
      matrix,
      labTarget,
      sampUnitSize,
      nPositive,
      prevalence
    ) %>% 
    distinct() %>% #keeping only distinct rows 
    arrange (desc(refID), targetSpecies, .by_group= TRUE)#, 


options(DT.options = list(scrollY="100vh",pageLength =10))

datatable(active,
            filter = "none", 
            rownames = F,
            colnames = c("refID","Country","Year","Target species",
                         "Sampling Point", "Reason for sampling", "Sampling strategy",
                         "matrix","Lab target","sample size","n Pos","prevalence"))


```



Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Survey</h1>

Row{data-height=800}
-----------------------------------------------------------------------

###



```{r survey}
survey <- dfDZ %>%
    filter(studyContext == "Survey (designed sampling)") %>%
    mutate(labTarget = case_when(str_detect(labTarget, "Ig.") ~ "Antibody", 
           TRUE ~ as.character(labTarget))) %>%
    select(
      refID,
      country,
      startYear,
      targetSpecies,
      sampPoint,
      reasonSampling,
      sampStrategy,
      matrix,
      labTarget,
      sampUnitSize,
      nPositive,
      prevalence
    ) %>% 
    distinct() %>% #keeping only distinct rows 
    arrange (desc(refID), targetSpecies, .by_group= TRUE)#, 


options(DT.options = list(scrollY="100vh",pageLength =10))

datatable(survey,
            filter = "none", 
            rownames = F,
            colnames = c("refID","Country","Year","Target species",
                         "Sampling Point", "Reason for sampling", "Sampling strategy",
                         "matrix","Lab target","sample size","n Pos","prevalence"))


```



Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;REFERENCES </h1>


Row
-----------------------------------------------------------------------
###
In the left panel you can find information about the entire systematic literature review. The specific references for this agent, and used in this section of the story map are listed below.

Row{data-height=600}
-----------------------------------------------------------------------

```{r}
 options(DT.options = list(scrollY="100vh",pageLength =5))
 datatable(unique(references[references$Refid%in%dfDZ$refID,c(1,3,6)]), filter = 'top', rownames=FALSE)


# kable(unique(references[references$Refid%in%dfDZ$refID,c(1,3,6)]), align="c",row.names = F)%>%
#   kable_material(c("striped", "hover"))

```
 


