---
title: "descriptive"
output: html_document
date: "2022-10-20"
---
# Setting up
```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
library(readxl)
```



```{r}
source("RUN-list-header.r")

dfgd <- read.csv("../data/FilesDownload/GeoDistribution_cleaned.csv")
references <- read.csv("../data/FilesDownload/GeoDistribution_refid.csv")

n.papers.total <- length(unique(dfgd$refID))
```

Geo distribution

i. Study info
ii. Animals/epidemiological unit
iii. Detection method
iv. Disease frequency measures



```{r}
for (a in 1:length(agents)){ 
      
      dfgd <- read.csv("../data/FilesDownload/GeoDistribution_cleaned.csv")
      agent <- agents[a] 
      dfDZ <- dfgd[dfgd$agent==agent,]
      n.papers <- length(unique(dfDZ$refID))
      out <- paste0(agents[a], " has ", n.papers, " papers.")
      print(out)
}
```


Host species
```{r}
for (a in 1:length(agents)){ 
      
      agent <- agents[a] 
      dfDZ <- dfgd[dfgd$agent==agent,]
      n.papers <- length(unique(dfDZ$refID))
      out <- paste0(agents[a], " has ", n.papers, " papers.")
      print(out)
}
```







```{r}
for(a in 1:length(agents)){
  
  cat(paste0("## [", a ,"] \n\n"))
  
agent <- agents[a]

  filtered = dfgd %>%
    filter(agent == agents[a]) 

  fig1 = filtered %>%
  group_by(studyContext, analysisYear) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = fct_reorder(studyContext, n), fill = studyContext)) +
    geom_bar()
  
  print(fig1)
  cat("\n\n")
  
}
```

How many studies are there per sampling context (types of studies)?

```{r setup, include=FALSE}
dftypesstudies <- dfgd %>%
  group_by(studyContext) %>%
  summarize(number = n()) %>%
  arrange(desc(number))


dftypesstudies 



```

Which agents were the most frequent?

```{r}
dfgd %>%
  group_by(agent) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
```

How many species were targeted per agent?

```{r}
dfgd %>%
  group_by(agent, 
           targetSpecies) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) 
#%>%
  #ggplot(mapping = aes(agent, n)) + 
           #geom_bar(stat = "identity")
```

Which countries present more studies reported? For which agents?

```{r}
dfgd %>%
  group_by(agent, 
           country) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
```

```{r}
R0table <- dfgd %>%
  filter(!is.na(R0)) %>%
  select(agent, 
         country, 
         sampArea, 
         studyContext, 
         startYear, 
         analysisYear, 
         R0, 
         lowerR0, 
         upperR0) %>%
  rename()

R0table1 <- head(R0table)
knitr::kable(R0table1, col.names = gsub("[.]", " ", names(R0table)))
  
```



#Animals/epidemiological unit

```{r}

animal <- dfgd %>% 
  select(targetSpecies,
    targetSpecies_C,
    sampPoint,
    sampPoint_C,
    sampStrategy,
    sampStrategy_C,
    longitudinal,
    sampUnit,
    sampUnit_C,
    sampUnitSize,
    minAgeMonths,
    maxAgeMonths) 

```

#Detection method
```{r}
dzDetec <- dfgd %>%
  select(
    refID,
    agent,
    matrix,
    matrix_C,
    labTest,
    labTest_C,
    labTarget,
    labTarget_C,
    labDescription,
    sensitivity,
    specificity) 


for (a in 1:length(agents)){ 
  cat(paste0("## [", a ,"] \n\n"))
  
  agent <- agents[a]
  
  tmp1 <- dzDetec %>%
    filter(#agent == "Rift Valley fever virus",
    agent == agents[a],
    !is.na(sensitivity | specificity)) %>%
    distinct(refID) %>%
    nrow()
  
 #n.sensSpec <- length(unique(tmp1$refID))

dzDetecprint <- paste0("From ", n.papers.total, " studies, ", tmp1, " have reported sensitivity and specificity results for ", agents[a],".")

print(dzDetecprint)
  cat("\n\n")
}
```



## Antibody
```{r}

detectiontb1 <- dfgd %>%
   filter(labTarget == "Antibody",
          nPositive != 0) %>% #fix
  select(
    refID,
    country,
    sampArea,
    nPositive,
    nNegative,
    sampUnitSize,
    labTest,
    #sensitivity,
    #specificity
        ) %>%
  rename(
    "Country" = country,
    "Sampled area" = sampArea,
    "Number of positives" = nPositive,
    "Number of negatives" = nNegative,
    "Samp unit size" = sampUnitSize,
    "Test" = labTest,
    #"Sensitivity" = sensitivity,
    #"Specificity" = specificity
  )

detectiontb <- head(detectiontb)
knitr::kable(detectiontb, col.names = gsub("[.]", " ", names(detectiontb)))

```





##Atg
```{r}
detectiontb2 <- dfgd %>%
   filter(labTarget == "Antigen",
          nPositive != 0) %>% #fix
  select(
    refID,
    country,
    sampArea,
    nPositive,
    nNegative,
    sampUnitSize,
    labTest,
    #sensitivity,
    #specificity
        ) %>%
  rename(
    "Country" = country,
    "Sampled area" = sampArea,
    "Number of positives" = nPositive,
    "Number of negatives" = nNegative,
    "Samp unit size" = sampUnitSize,
    "Test" = labTest,
    #"Sensitivity" = sensitivity,
    #"Specificity" = specificity
  )

detectiontb2 <- head(detectiontb2)
knitr::kable(detectiontb2, col.names = gsub("[.]", " ", names(detectiontb2)))

```


#Disease frequency measures given

```{r}

dzFreq <- dfgd %>%
    select(
    refID,
    agent,
    nPositive,
    imported,
    nNegative,
    disFreedom,
    prevalence,
    UCI_prev,
    LCI_prev,
    incidence,
    UCI_incid,
    LCI_incid,
    incidUnit,
    incidUnit2,
    R0,
    lowerR0,
    upperR0,
    impactMeasure,
    impactValue,
    impactUnit,
    clinicalSigns,
    severity,
    moreInfo,
    riskFactors,
    protectiveFactors,
    moreInfo2)

#We should report clinical signs only from studies that would do so, though. 

for (a in 1:length(agents)){ 
  cat(paste0("## [", a ,"] \n\n"))
  
  agent <- agents[a]
  
  n.clinSigns <- dzFreq %>%
  filter(!is.na(clinicalSigns),
         agent == agents[a]) %>%
  distinct(refID) %>%
  nrow()

dzClinSigns <- paste("From", n.papers.total,"studies, ", n.clinSigns, "have reported clinical signs for", agents[a],".")

print(dzClinSigns)
  cat("\n\n")
}

```


