---
title: "Evidence from systematic literature review"
params:
    agent: "agent"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    self_contained: false

---
<style type="text/css">

body{
  font-family: Verdana;
  font-size: 12pt;
}

.navbar {
  background-color:#1DAF8E;
}

.bggreen {
  background-color: #1DAF8E;
}

/* Headers */
h1{
  font-family: Verdana;
  font-size: 16pt;
  font-weight: bold; 
  color: white;
}

.chart-title {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li.active a {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
    font-size: 16pt;
}


</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, fig.width=10,fig.height=6)
library(plotly)
library(dplyr)
library(stringr)
library(knitr)
library(gdata)
library(kableExtra)
library(DT)
library(flexdashboard)

source("Functions.r")


dfva <- read.csv("../data/FilesDownload/Vaccines_cleaned.csv")
references <- read.csv("../data/FilesDownload/Vaccines_refid.csv")

agent <- params$agent 

# styling=T
# min.groups.plot=1
# agent = agents[a]
# agent.subtype <- agent.subtypes[a]


dfDZ <- dfva[dfva$agent==agent,]


dfDZ$targetSpecies <- gsub("\\s*\\([^\\)]+\\)","",as.character(dfDZ$targetSpecies))
dfDZ <- species.name.cleanup(data=dfDZ)

references$targetSpecies<- gsub("\\s*\\([^\\)]+\\)","",as.character(references$targetSpecies))
references <- species.name.cleanup(data=references)


dfDZ$targetSpecies <- as.factor(dfDZ$targetSpecies)


plots.font <- list(
  family="Verdana",
  size=16
)


dzeff <- dfDZ[which(!is.na(dfDZ$efficacy)),]
dzcov <- dfDZ[which(!is.na(dfDZ$coverage)),]


#table(dfDZ$targetSpecies)
```




Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Reported Vaccine efficacy </h1>



```{r, results='asis'}
if(length(unique(dzeff$refID))>0){
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, of which ",length(unique(dzeff$refID)),"  reported vaccine efficacy. The results are presented in the table below.\n"))
  cat("\nAll references, and the species they studied, are listed further below in the complete reference list.\n")
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy will be summarized and displayed in this story map.\n")

  
  cat("\nRow{data-height=600}\n")
cat("\n-----------------------------------------------------------------------\n")

options(DT.options = list(scrollY="100vh",pageLength =5))
datatable(dzeff[,c("refID","targetSpecies","testSubstance",
                    "efficacy","vaccineType","route","dose1")])

}else{
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, but NONE reported  vaccine efficacy explicitly.\n"))
  cat("\nAll references, and the species they studied, are listed further below in the complete reference list.\n")
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy will be summarized and displayed in this story map.\n")

}

```






Row{data-height=60 .bggreen}
-----------------------------------------------------------------------

<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Reported Vaccine coverage </h1>


```{r, results='asis'}
if(length(unique(dzcov$refID))>0){
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, of which ",length(unique(dzcov$refID)),"  reported vaccine efficacy. The results are presented in the table below.\n"))
  cat("\nAll references, and the species they studied, are listed further below in the complete reference list.\n")
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy will be summarized and displayed in this story map.\n")

  
  cat("\nRow{data-height=600}\n")
cat("\n-----------------------------------------------------------------------\n")

options(DT.options = list(scrollY="100vh",pageLength =5))
datatable(dzeff[,c("refID","targetSpecies","testSubstance",
                    "coverage","vaccineType","route","dose1")])

}else{
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, but NONE reported  vaccine efficacy explicitly.\n"))
  cat("\nAll references, and the species they studied, are listed further below in the complete reference list.\n")
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy will be summarized and displayed in this story map.\n")

}

```










Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;REFERENCES </h1>


Row
-----------------------------------------------------------------------
###
In the left panel you can find information about the entire systematic literature review. The specific references for this agent, and used in this section of the story map are listed below.

Row{data-height=600}
-----------------------------------------------------------------------

```{r references}
options(DT.options = list(scrollY="100vh",pageLength =5))
datatable(unique(references[references$Refid%in%dfDZ$refID,c(1,3,5)]), filter = 'top', rownames=FALSE)

```
 
 
