---
title: "Evidence from systematic literature review"
params:
    agent: "agent"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    self_contained: false

---
<style type="text/css">

body{
  font-family: Verdana;
  font-size: 12pt;
}

.navbar {
  background-color:#1DAF8E;
}

.bggreen {
  background-color: #1DAF8E;
}

/* Headers */
h1{
  font-family: Verdana;
  font-size: 16pt;
  font-weight: bold; 
  color: white;
}

.chart-title {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li.active a {
    font-size: 16pt;
}

.nav-tabs-custom .nav-tabs li:not(.active) a {
    font-size: 16pt;
}


</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, fig.width=10,fig.height=6)
library(plotly)
library(dplyr)
library(stringr)
library(knitr)
library(gdata)
library(kableExtra)
library(DT)
library(flexdashboard)

source("Functions.r")


dfva <- read.csv("../data/FilesDownload/Vaccines_cleaned.csv")
references <- read.csv("../data/FilesDownload/Vaccines_refid.csv")

agent <- params$agent 

# styling=T
# min.groups.plot=1
# agent = agents[a]
# agent.subtype <- agent.subtypes[a]


dfDZ <- dfva[dfva$agent==agent,]


dfDZ$targetSpecies <- gsub("\\s*\\([^\\)]+\\)","",as.character(dfDZ$targetSpecies))
dfDZ <- species.name.cleanup(data=dfDZ)

references$targetSpecies<- gsub("\\s*\\([^\\)]+\\)","",as.character(references$targetSpecies))
references <- species.name.cleanup(data=references)


dfDZ$targetSpecies <- as.factor(dfDZ$targetSpecies)


plots.font <- list(
  family="Verdana",
  size=16
)

eff.refid <- unique(dfDZ$refID[which(!is.na(dfDZ$efficacy))])
cov.refid <- unique(dfDZ$refID[which(!is.na(dfDZ$coverage))])


dzeff <- dfDZ[dfDZ$refID%in%eff.refid,]
dzcov <- dfDZ[dfDZ$refID%in%cov.refid,]


#table(dfDZ$targetSpecies)
```




Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Reported Vaccine efficacy </h1>



```{r, results='asis'}
if(length(unique(dzeff$refID))>0){
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, of which ",length(unique(dzeff$refID)),"  reported vaccine efficacy. The results are presented in the table below.\n"))
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy and coverage will be summarized and displayed in this story map.\n")

  
  cat("\nRow\n")
cat("\n-----------------------------------------------------------------------\n")
 cat("\n### \n")
# options(DT.options = list(scrollY="100vh",pageLength =5))
# datatable(unique(dzeff[dzeff$testSubstance!="Unvaccinated control",c("refID","targetSpecies","testSubstance",
#                     "efficacy","vaccineType","route","dose1")]))
 table.data <- unique(dzeff[dzeff$testSubstance!="Unvaccinated control",c("refID","targetSpecies","testSubstance",
                    "coverage","vaccineType","route","days.lastdose.atchallenge","dose1")])%>%
  arrange(targetSpecies,vaccineType,testSubstance,efficacy,route)
colnames(table.data)<- c("uniqueID","Species","Vaccine","Efficacy %","Type","Route","Days from last dose to challenge","Dose")

kable(table.data, align="c",row.names = F)%>%
    kable_styling()

}else{
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, but NONE reported  vaccine efficacy explicitly.\n"))
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy and coverage will be summarized and displayed in this story map.\n")

}

```






Row{data-height=60 .bggreen}
-----------------------------------------------------------------------

<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Reported Vaccine coverage </h1>


```{r, results='asis'}
if(length(unique(dzcov$refID))>0){
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, of which ",length(unique(dzcov$refID)),"  reported vaccine coverage The results are presented in the table below.\n"))
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy ad coverage will be summarized and displayed in this story map.\n")

  
  cat("\nRow\n-----------------------------------------------------------------------\n")
cat("\n### \n")
#options(DT.options = list(scrollY="100vh",pageLength =10))
#datatable(unique(dzcov[dzcov$testSubstance!="Unvaccinated control",c("refID","targetSpecies","testSubstance",
#                    "coverage","vaccineType","route","dose1")]))

table.data <- unique(dzcov[dzcov$testSubstance!="Unvaccinated control",c("refID","targetSpecies","testSubstance",
                    "coverage","vaccineType","route","days.lastdose.atchallenge","dose1")])%>%
  arrange(targetSpecies,vaccineType,testSubstance,coverage,route)
colnames(table.data)<- c("uniqueID","Species","Vaccine","Coverage %","Type","Route","Days from last dose to challenge","Dose")
kable(table.data, align="c",row.names = F)%>%
    kable_styling()

}else{
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat(paste0("\nA total of ",length(unique(dfDZ$refID))," references were reviewed, but NONE reported  vaccine coverage explicitly.\n"))
  cat("\nIn the next round of updates of the systematic literature reviews for vaccines (planned for 2023), outcomes other than efficacy and coverage will be summarized and displayed in this story map.\n")

}

```




```{r, results='asis'}
if(length(unique(dzcov$refID))|length(unique(dzeff$refID))>0){
  cat("\nRow{data-height=60 .bggreen}\n-----------------------------------------------------------------------\n")
  cat("\n<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;References reporting other results </h1>\n")
  
  cat("\nRow\n-----------------------------------------------------------------------\n")
  cat("\n### \n")
   cat("\nThe table below lists all studies which were reviewed, but which did not report vaccine efficacy or coverage explicitly.\n")

  
  cat("\nRow\n-----------------------------------------------------------------------\n")
cat("\n### \n")

dfDZ2 <- dfDZ[!dfDZ$refID%in%eff.refid,]
dfDZ2 <- dfDZ2[!dfDZ2$refID%in%cov.refid,]

# options(DT.options = list(scrollY="100vh",pageLength =5))
# datatable(unique(dfDZ2[dfDZ2$testSubstance!="Unvaccinated control",c("refID","targetSpecies","testSubstance",
#                     "vaccineType","route","dose1")]))

table.data <- unique(dfDZ2[dfDZ2$testSubstance!="Unvaccinated control",c("refID","targetSpecies","testSubstance",
                     "vaccineType","route","days.lastdose.atchallenge","dose1")])%>%
  arrange(targetSpecies,vaccineType,testSubstance,route)
colnames(table.data)<- c("uniqueID","Species","Vaccine","Type","Route","Days from last dose to challenge","Dose")
kable(table.data, align="c",row.names = F)%>%
    kable_styling()

}

```









Row{data-height=60 .bggreen}
-----------------------------------------------------------------------


<h1> &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;REFERENCES </h1>


Row
-----------------------------------------------------------------------
###
In the left panel you can find information about the entire systematic literature review. The specific references for this agent, and used in this section of the story map are listed below.

Row{data-height=800}
-----------------------------------------------------------------------

```{r references}
options(DT.options = list(scrollY="100vh",pageLength =5))
datatable(unique(references[references$Refid%in%dfDZ$refID,c(1,3,5)]), filter = 'top', rownames=FALSE)

```
 
 
